An Open-Source Implementation of the CMPS Algorithm for Assessing Similarity of Bullets

### 2022-03-27 submissions/resubmission-ju-hofmann2/ju-hofmann.tex
ready for parallel testing on Windows

cmps.result.KM <- extract_feature_cmps(sig1, sig2)
cmps.result.KNM <- extract_feature_cmps(sig1, sig3)
\end{Sinput}
\end{Schunk}

@@

  \begin{itemize}
  \item
    \textbf{Calculate the cross-correlation curve:} Calculate the
    cross-correlation curve between a basis segment \code{x} and the
    reference signature \code{y} using the function
    \code{get\_ccf4(x, y, ...)} as shown in \autoref{fig:segplot2}. The
    position indicates the lag by which a basis segment is moved with
    respect to its original placement. A position is considered ``good''
    if it results in a peak in the cross-correlation between the basis
    segment and the reference.
  \item
    \textbf{Correlation peaks:} Two strategies referred to as
    ``multi-peak inspection'' and ``multi-peak inspection at different
    segment lengths'' in \citet{cmps} are used for identifying positions
    of correlation peaks as candidate positions. The latter is also
    called ``multi-segment lengths strategy''. The parameter
    \code{npeaks.set} in \code{extract\_feature\_cmps(...)} determines
    which strategy to use and the number of candidate positions:

    \begin{itemize}
    \tightlist
    \item
      If \code{npeaks.set} is an integer vector of length 1, for example
      \code{npeaks.set = 5}, the positions of the top five peaks in the
      cross-correlation curve are identified as candidate positions for
      registration.
    \item
      If \code{npeaks.set} is an integer vector of length more than 1,
      for example \code{npeaks.set = c(5, 3, 1)}, the multi-segment
      lengths strategy will be used: calculate the cross-correlation
      function between a basis segment and the reference and identify
      positions of the top five peaks; double the segment length to a
      specified value, re-calculate the cross-correlation function, and
      identify three peaks; repeat this process and identify a single
      peak in the newly computed cross-correlation function.
      \autoref{fig:seg_all} shows an example of three levels of basis
      segment 6 and their corresponding cross-correlation curves and
      identified peaks. Note that in \citet{cmps} the segment length is
      doubled at each level of a basis segment, but in the present
      implementation users are allowed to choose the segment length at
      each level.
    \item
      \code{get\_ccr\_peaks(comp, segments, seg\_outlength, nseg = 1, npeaks = 5)}
      computes the cross-correlation curve between a basis or increased
      segment and the reference signature and finds peaks in the
      cross-correlation curve. The number of peaks detected is equal to
      \code{npeaks}, which is an integer. \code{segments},
      \code{seg\_outlength}, and \code{nseg} determines the segment in
      the cross-correlation computation, and \code{comp} gives the
      reference signature. If the multi-segment lengths strategy is
      used, then \code{get\_ccr\_peaks(...)} is called in a
      \code{lapply()} for each level of the basis segment. The resulting
      list is called \code{ccr.list}.
    \end{itemize}
  \item
    \textbf{multi-segment lengths strategy:} with the multi-segment
    lengths strategy being used, a position is identified as a candidate
    position for registration and is called as a ``consistent
    correlation peak'' if it results in a top peak in the
    cross-correlation curve with a tolerance zone determined by
    \code{Tx} in all segment levels. Note that in \citet{cmps}, a
    segment at its largest scale (highest level) always identifies one
    peak, but we do not have this requirement in our implementation.

    \begin{itemize}
    \tightlist
    \item
      the function \code{get\_seg\_scale(segments, nseg, out\_length)}
      is used to obtain the (potentially increased) version of a basis
      segment. \code{segments}, which is a list containing all basis
      segments generated by the function \code{get\_segs(...)} in step
      1, and \code{nseg} are used to determine the basis segment to be
      increased. \code{out\_length} specifies the length of the output
      segment.
    \item
      \code{get\_ccp(ccr.list, Tx = 25)} tries to identify the
      ``consistent correlation peak''. \code{ccr.list} is the result of
      \code{lapply()} and \code{get\_ccr\_peaks(...)}, and \code{Tx}
      determines the size of a tolerance zone used in identifying the
      consistent correlation peak. \code{get\_ccp(...)} returns
      \code{NULL} if there is no consistent correlation peak.
    \end{itemize}
  \end{itemize}
\item
  \textbf{determine the congruent registration position:} A candidate
  position ``receives'' votes from basis segments that identify it or a
  close position within a tolerance zone of \code{Tx} as a candidate
  position in step 2. Votes for all candidate positions are tallied, and
  the position with the highest number of votes gets chosen as the
  \emph{congruent registration position}, indicating that most of the
  basis segments find their highly similar counterpart in the reference
  signature in terms of correlation at this registration position. In
  case of ties the middle position is taken as the congruent
  registration position. Basis segments with a congruent registration
  position are called ``congruent matching profile segments'' (CMPS).
  The total number of CMPS is the CMPS score of the comparison.
  \code{get\_CMPS(input.ccp, Tx = 25)} is the function that tallies the
  votes and determines the congruent registration position and congruent
  matching profile segments (CMPS).
\end{enumerate}

Note that there are several parameters in the CMPS algorithm that are
left to the users to decide, such as the length of basis segments
\code{seg\_length} in step 1, the number of peaks \code{npeaks.set}
identified on each level in step 2, and the length of the tolerance zone
\code{Tx} in both step 2 and 3. In our implementation of the CMPS
algorithm we used the parameters given in the original CMPS paper
\citep{cmps} as the default values for these parameters. However, the
authors state that no cross-validation has been done - there might be
also issues with respect to resolution of the scans. Further research is
needed, until then users are advised to think of default values as
starting values and consider alternatives. The main function that
combines all steps in the CMPS algorithm described above is called
\code{extract\_feature\_cmps(...)}. Here we present it with its default
parameters.

\begin{Schunk}
\begin{Sinput}
extract_feature_cmps(
  x,
  y,
  seg_length = 50,
  Tx = 25,
  npeaks.set = c(5, 3, 1),
  include = NULL,
  outlength = NULL
)
\end{Sinput}
\end{Schunk}

The function \code{extract\_feature\_cmps} allows for the following
input from users besides the previously discussed parameters
\code{seg\_length}, \code{npeaks.set}, and \code{Tx}:

\begin{itemize}
\item
  \code{x} and \code{y} are two signatures: \code{x} serves as the
  comparison signature (which will be divided into basis segments) and
  \code{y} is the reference signature;
\item
  \code{include} determines the format of the function result. Besides
  the \code{CMPS.score}, other aspects of the comparison help in
  understanding how the \code{CMPS.score} is computed. By default
  \code{include} is set to \code{NULL} and only the \code{CMPS.score} is
  returned; further results are included when \code{include} is (an
  abbreviation of) one of or a vector of the following strings:
  \code{"nseg"}, \code{"congruent.pos"}, \code{"congruent.seg.idx"},
  \code{"segments"}, \code{"parameters"}, and \code{"full\_result"}. If
  \code{include} is specified as \code{"full\_result"} (or its
  abbreviation), the output includes everything listed below.

  \begin{itemize}
  \tightlist
  \item
    \code{nseg}: the number of basis segments from the comparison
    signature; this is also the highest possible CMPS score of the
    comparison;
  \item
    \code{congruent.pos}: the congruent registration position;
  \item
    \code{congruent.seg.idx}: the indices of all congruent matching
    profile segments;
  \item
    \code{ccp.list}: a list showing identified candidate positions of
    all basis segments;
  \item
    \code{pos.df}: a data frame containing all candidate positions and
    their respective number of votes;
  \item
    \code{segments}: a list containing all basis segments;
  \item
    \code{parameters}: a list containing all input arguments of
    \code{extract\_feature\_cmps};
  \end{itemize}
\item
  \code{outlength} specifies the segment length of a basis segment at
  each level under the multi-segment lengths strategy. By default
  \code{outlength} is set to \code{NULL}, indicating that a basis
  segment should double its segment length at the next level and
  conforming to the description in \citet{cmps} .
\end{itemize}

@@

# algorithm with multi-peak insepction at three different segment levels
cmps_with_multi_scale <- 
  extract_feature_cmps(sigs1$sig, sigs2$sig, 
                       npeaks.set = c(5,3,1), include = "full_result")

# algorithm with multi-peak inspection at the basis scale only
cmps_without_multi_scale <- 
  extract_feature_cmps(sigs1$sig, sigs2$sig, 
                       npeaks.set = 5, include = "full_result")
\end{Sinput}
\end{Schunk}

In the first example, \code{npeaks.set} is a vector of three integers,
i.e.~the algorithm uses the multi-segment lengths strategy to create the
result object \code{cmps\_with\_multi\_scale}. For
\code{cmps\_without\_multi\_scale} each basis segment is linked to the
top 5 candidate positions. We use \code{include = "full\_result"} to
capture all results. In this example, the CMPS is 9 when using multiple
segments, and 12 when using a single segment. As discussed in
\citet{cmps}, using multi-segment lengths strategy can reduce the number
of false positives when identifying candidate positions; however, any
score based method is walking the line between false positives and false
negatives. As the number of false positives is reduced the number of
false negatives might rise. More discussion and comparisons between the
two versions of the CMPS algorithm will be presented in later sections.
Note, that the multi-segment lengths method is slower because the
algorithm is run once for each segment length.

@@

{\small {}
\begin{Schunk}
\begin{Sinput}
sig.plot <- cmps_signature_plot(
  cmps_with_multi_scale
)
sig.plot$segment_shift_plot
\end{Sinput}
\end{Schunk}
}
\vspace{1em}
\end{minipage}
\begin{minipage}{.59\textwidth}
\includegraphics[width=\textwidth]{ju-hofmann_files/figure-latex/sigplot-1.pdf}
\end{minipage}
\end{adjustbox}
\end{subfigure}
\begin{subfigure}[t]{\textwidth}
\caption{\label{fig:sigplot2}The black line shows the reference signature; the red line shows the comparison signature. Solid part shows the congruent matching profile segments, and the dashed part shows segments that do not agree with the congruent registration position.}
\vspace{1em}
\begin{adjustbox}{valign=t}
\begin{minipage}{.39\textwidth}

{\small {}
\begin{Schunk}
\begin{Sinput}
sig.plot$signature_shift_plot
\end{Sinput}
\end{Schunk}
}
\vspace{1em}
\end{minipage}
\begin{minipage}{.59\textwidth}
\includegraphics[width=\textwidth]{ju-hofmann_files/figure-latex/sigplot2-1.pdf}
\end{minipage}
\end{adjustbox}
\end{subfigure}
\caption{\label{fig:sigplots} Two visual outputs of cmps\_signature\_plot()}
\end{figure}

@@

\begin{Schunk}
\begin{Sinput}
sig.plot$seg_shift
\end{Sinput}
\begin{Soutput}
#>    seg.idx seg.shift
#> 7        7         0
#> 8        8        -1
#> 14      14         5
#> 16      16         8
#> 17      17         8
#> 18      18         8
#> 19      19         9
#> 20      20         9
#> 22      22        12
\end{Soutput}
\end{Schunk}

While \code{cmps\_signature\_plot()} focuses on the signature level,
\code{cmps\_segment\_plot()} focuses on the segment level. It provides
the ``full result'' of \code{extract\_feature\_cmps()}, but also takes
an argument, \code{seg.idx}, indicating which segment should be
inspected. When checking \code{sig.plot\$seg\_shift} we notice that
segment number 6 is not one of the congruent matching profile segments.
We can therefore set \code{seg.idx = 6} in \code{cmps\_segment\_plot()}
and investigate the reason why this segment disagrees with the congruent
registration position.

@@

\begin{itemize}
\tightlist
\item
  \autoref{fig:segplot} is the \code{segment\_plot} for basis segment 6
  at level one (in its original length). We used
  \code{npeaks.set = c(5, 3, 1)} in \code{extract\_feature\_cmps()} when
  calculating the CMPS score. Therefore the top five peaks are
  identified in the cross-correlation curve at level one. Segment 6 is
  plotted at the positions where these 5 peaks are identified with
  dashed lines in the \code{segment\_plot}. The solid thick black line
  shows the segment at its original position (which in this example is
  very close to the actual registration position).
\item
  \autoref{fig:segplot2} is the \code{scale\_ccf\_plot} of basis segment
  6 at level one. It shows the cross-correlation curve computed by the
  reference signature and the level-one basis segment 6. The five
  highest peaks are marked by dots on the curve.
\end{itemize}

@@

{\small {}
\begin{Schunk}
\begin{Sinput}
seg.plot <- cmps_segment_plot(
  cmps_with_multi_scale, 
  seg.idx = 6
)
seg.plot[[1]]$segment_plot
\end{Sinput}
\end{Schunk}
}
\vspace{1em}
\end{minipage}
\begin{minipage}{.59\textwidth}
\includegraphics[width=\textwidth]{ju-hofmann_files/figure-latex/segplot-1.pdf}
\end{minipage}
\end{adjustbox}
\end{subfigure}
\begin{subfigure}[t]{\textwidth}
\caption{\label{fig:segplot2}scale\_ccf\_plot shows the cross-correlation curve between the reference signature and segment 6 at level one. The five highest peaks are marked by dots. The vertical red dashed line indicates the congruent registration position; the green dashed line shows a peak position in the highest segment level; the blue dashed lines show the tolerance zone around the green dashed line. We can see that none of the five highest peaks at level one falls within the tolerance zone, indicating that there is no consistent correlation peak or a candidate position identified by basis segment 6 under the multi-segment lengths strategy. Thus, the basis segment 6 doesn't vote for the congruent registration position and is not a cmps.}
\vspace{1em}
\begin{adjustbox}{valign=t}
\begin{minipage}{.39\textwidth}

{\small {}
\begin{Schunk}
\begin{Sinput}
seg.plot[[1]]$scale_ccf_plot
\end{Sinput}
\end{Schunk}
}
\vspace{1em}
\end{minipage}
\begin{minipage}{.59\textwidth}
\includegraphics[width=\textwidth]{ju-hofmann_files/figure-latex/segplot2-1.pdf}
\end{minipage}
\end{adjustbox}
\end{subfigure}
\caption{\label{fig:segplots} Two plots used to investigate basis segment 6 at level one}
\end{figure}

@@

ggarrange(
  plotlist = 
    unlist(seg.plot, 
           recursive = FALSE),
  ncol = 2, 
  nrow = 3)
\end{Sinput}
\end{Schunk}
}
\vspace{1em}
\end{minipage}
\begin{minipage}{.59\textwidth}
\includegraphics[width=\textwidth]{ju-hofmann_files/figure-latex/segplot3-1.pdf}
\end{minipage}
\end{adjustbox}
\caption{\label{fig:seg_all} Put segment\_plot and scale\_ccf\_plot of all three levels together. We are identifying five highest peaks at level one, three peaks at level two, and one peak at level three since npeaks.set = c(5, 3, 1). The highest peak position at level three is marked by the green dashed line across all segment levels. However, the highest peak on level three does not coincide with any of the top five highest peaks at level one. This indicates that there is no consistent correlation peak or a candidate position for basis segment 6 under the multi-segment lengths strategy.}
\end{figure}

@@

\begin{Schunk}
\begin{Sinput}
extract_feature_cmps(
  x, y,
  seg_length = 50,
  Tx = 25,
  npeaks.set = c(5,3,1),
  include = "nseg"
)
\end{Sinput}
\end{Schunk}

@@

\caption{Distribution of $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ for Hamby 252; outliers are removed in bullet signatures; \texttt{seg\_length = 50}, \texttt{Tx = 25}, \texttt{npeaks.set = c(5,3,1)} }\label{fig:result1_252}
\end{figure}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
extract_feature_cmps(
  x, y,
  seg_length = 61, 
  Tx = 30,
  npeaks.set = c(5,3,1),
  include = "nseg"
)
\end{Sinput}
\end{Schunk}

@@

\caption{Distribution of $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ for Hamby 44; outliers are removed in bullet signatures; \texttt{seg\_length = 61}, \texttt{Tx = 30}, \texttt{npeaks.set = c(5,3,1)} }\label{fig:result1_44}
\end{figure}
\end{Schunk}

@@

We investigated the effects of different sets of parameters at the
example of both Hamby sets 252 and 44. More specifically, we
investigated the separation achieved using the \pkg{cmpsR}
implementation under various segment lengths (controlled by the
parameter \code{seg\_length}). Specifically, we fixed the parameter
\code{npeaks.set} that controls the number of peaks at each segment
level to be \code{npeaks.set = c(5,3,1)} and modified the parameter
\code{seg\_length}. \autoref{fig:param_seg_plot} shows that the default
values of \code{seg\_length} for Hamby 252 and Hamby 44 (50 for Hamby
252 and 61 for Hamby 44, which represent 78.125 \textmu m and 78.69
\textmu m, respectively) result in high values of the sum of squares
ratio, no matter which CMPS metrics are used for an evaluation. However,
we also see, that for Hamby set 252 a basis segment length of 75 is a
better choice than the default segment length; a basis segment length of
122 results in a higher value of sum of squares ratio for Hamby 44.

\autoref{fig:param_npeak_plot} shows results of the CMPS algorithm using
different strategies for identifying peaks in the correlation structure
between signatures. Basis segment length is fixed to the default level
for this evaluation. As can be seen in \autoref{fig:param_npeak_plot},
the default value of \code{npeaks.set} (\code{npeaks.set = c(5,3,1)})
leads to promising results in terms of the sum of squares ratio;
however, other choices of \code{npeaks.set} match and exceed this sum of
squares ratio value.

>>>>

cmps_result_KM <- extract_feature_cmps(sig1, sig2)
cmps_result_KNM <- extract_feature_cmps(sig1, sig3)
\end{Sinput}
\end{Schunk}

@@

  \begin{itemize}
  \item
    \textbf{Calculate the cross-correlation curve:} Calculate the
    cross-correlation curve between a basis segment \code{x} and the
    reference signature \code{y} using the function
    \code{get\_ccf4(x, y, ...)} as shown in \autoref{fig:segplot2}. The
    position indicates the lag by which a basis segment is moved with
    respect to its original placement. A position is considered ``good''
    if it results in a peak in the cross-correlation between the basis
    segment and the reference.
  \item
    \textbf{Correlation peaks:} Two strategies referred to as
    ``multi-peak inspection'' and ``multi-peak inspection at different
    segment lengths'' in \citet{cmps} are used for identifying positions
    of correlation peaks as candidate positions. The latter is also
    called ``multi-segment lengths strategy''. The parameter
    \code{npeaks\_set} in \code{extract\_feature\_cmps(...)} determines
    which strategy to use and the number of candidate positions:

    \begin{itemize}
    \tightlist
    \item
      If \code{npeaks\_set} is an integer vector of length 1, for
      example \code{npeaks\_set = 5}, the positions of the top five
      peaks in the cross-correlation curve are identified as candidate
      positions for registration.
    \item
      If \code{npeaks\_set} is an integer vector of length more than 1,
      for example \code{npeaks\_set = c(5, 3, 1)}, the multi-segment
      lengths strategy will be used: calculate the cross-correlation
      function between a basis segment and the reference and identify
      positions of the top five peaks; double the segment length to a
      specified value, re-calculate the cross-correlation function, and
      identify three peaks; repeat this process and identify a single
      peak in the newly computed cross-correlation function.
      \autoref{fig:seg_all} shows an example of three levels of basis
      segment 6 and their corresponding cross-correlation curves and
      identified peaks. Note that in \citet{cmps} the segment length is
      doubled at each level of a basis segment, but in the present
      implementation users are allowed to choose the segment length at
      each level.
    \item
      \code{get\_ccr\_peaks(comp, segments, seg\_outlength, nseg = 1, npeaks = 5)}
      computes the cross-correlation curve between a basis or increased
      segment and the reference signature and finds peaks in the
      cross-correlation curve. The number of peaks detected is equal to
      \code{npeaks}, which is an integer. \code{segments},
      \code{seg\_outlength}, and \code{nseg} determines the segment in
      the cross-correlation computation, and \code{comp} gives the
      reference signature. If the multi-segment lengths strategy is
      used, then \code{get\_ccr\_peaks(...)} is called in a
      \code{lapply()} for each level of the basis segment. The resulting
      list is called \code{ccr\_list}.
    \end{itemize}
  \item
    \textbf{multi-segment lengths strategy:} with the multi-segment
    lengths strategy being used, a position is identified as a candidate
    position for registration and is called as a ``consistent
    correlation peak'' if it results in a top peak in the
    cross-correlation curve with a tolerance zone determined by
    \code{Tx} in all segment levels. Note that in \citet{cmps}, a
    segment at its largest scale (highest level) always identifies one
    peak, but we do not have this requirement in our implementation.

    \begin{itemize}
    \tightlist
    \item
      the function \code{get\_seg\_scale(segments, nseg, out\_length)}
      is used to obtain the (potentially increased) version of a basis
      segment. \code{segments}, which is a list containing all basis
      segments generated by the function \code{get\_segs(...)} in step
      1, and \code{nseg} are used to determine the basis segment to be
      increased. \code{out\_length} specifies the length of the output
      segment.
    \item
      \code{get\_ccp(ccr\_list, Tx = 25)} tries to identify the
      ``consistent correlation peak''. \code{ccr\_list} is the result of
      \code{lapply()} and \code{get\_ccr\_peaks(...)}, and \code{Tx}
      determines the size of a tolerance zone used in identifying the
      consistent correlation peak. \code{get\_ccp(...)} returns
      \code{NULL} if there is no consistent correlation peak.
    \end{itemize}
  \end{itemize}
\item
  \textbf{determine the congruent registration position:} A candidate
  position ``receives'' votes from basis segments that identify it or a
  close position within a tolerance zone of \code{Tx} as a candidate
  position in step 2. Votes for all candidate positions are tallied, and
  the position with the highest number of votes gets chosen as the
  \emph{congruent registration position}, indicating that most of the
  basis segments find their highly similar counterpart in the reference
  signature in terms of correlation at this registration position. In
  case of ties the middle position is taken as the congruent
  registration position. Basis segments with a congruent registration
  position are called ``congruent matching profile segments'' (CMPS).
  The total number of CMPS is the CMPS score of the comparison.
  \code{get\_CMPS(input\_ccp, Tx = 25)} is the function that tallies the
  votes and determines the congruent registration position and congruent
  matching profile segments (CMPS).
\end{enumerate}

Note that there are several parameters in the CMPS algorithm that are
left to the users to decide, such as the length of basis segments
\code{seg\_length} in step 1, the number of peaks \code{npeaks\_set}
identified on each level in step 2, and the length of the tolerance zone
\code{Tx} in both step 2 and 3. In our implementation of the CMPS
algorithm we used the parameters given in the original CMPS paper
\citep{cmps} as the default values for these parameters. However, the
authors state that no cross-validation has been done - there might be
also issues with respect to resolution of the scans. Further research is
needed, until then users are advised to think of default values as
starting values and consider alternatives. The main function that
combines all steps in the CMPS algorithm described above is called
\code{extract\_feature\_cmps(...)}. Here we present it with its default
parameters.

\begin{Schunk}
\begin{Sinput}
extract_feature_cmps(
  x,
  y,
  seg_length = 50,
  Tx = 25,
  npeaks_set = c(5, 3, 1),
  include = NULL,
  outlength = NULL
)
\end{Sinput}
\end{Schunk}

The function \code{extract\_feature\_cmps} allows for the following
input from users besides the previously discussed parameters
\code{seg\_length}, \code{npeaks\_set}, and \code{Tx}:

\begin{itemize}
\item
  \code{x} and \code{y} are two signatures: \code{x} serves as the
  comparison signature (which will be divided into basis segments) and
  \code{y} is the reference signature;
\item
  \code{include} determines the format of the function result. Besides
  the \code{CMPS\_score}, other aspects of the comparison help in
  understanding how the \code{CMPS\_score} is computed. By default
  \code{include} is set to \code{NULL} and only the \code{CMPS\_score}
  is returned; further results are included when \code{include} is (an
  abbreviation of) one of or a vector of the following strings:
  \code{"nseg"}, \code{"congruent\_pos"}, \code{"congruent\_seg\_idx"},
  \code{"segments"}, \code{"parameters"}, and \code{"full\_result"}. If
  \code{include} is specified as \code{"full\_result"} (or its
  abbreviation), the output includes everything listed below.

  \begin{itemize}
  \tightlist
  \item
    \code{nseg}: the number of basis segments from the comparison
    signature; this is also the highest possible CMPS score of the
    comparison;
  \item
    \code{congruent\_pos}: the congruent registration position;
  \item
    \code{congruent\_seg\_idx}: the indices of all congruent matching
    profile segments;
  \item
    \code{ccp\_list}: a list showing identified candidate positions of
    all basis segments;
  \item
    \code{pos\_df}: a data frame containing all candidate positions and
    their respective number of votes;
  \item
    \code{segments}: a list containing all basis segments;
  \item
    \code{parameters}: a list containing all input arguments of
    \code{extract\_feature\_cmps};
  \end{itemize}
\item
  \code{outlength} specifies the segment length of a basis segment at
  each level under the multi-segment lengths strategy. By default
  \code{outlength} is set to \code{NULL}, indicating that a basis
  segment should double its segment length at the next level and
  conforming to the description in \citet{cmps} .
\end{itemize}

@@

# algorithm with multi-peak insepction at three different segment levels
cmps_with_multi_scale <-
  extract_feature_cmps(sigs1$sig, sigs2$sig,
    npeaks_set = c(5, 3, 1), include = "full_result"
  )

# algorithm with multi-peak inspection at the basis scale only
cmps_without_multi_scale <-
  extract_feature_cmps(sigs1$sig, sigs2$sig,
    npeaks_set = 5, include = "full_result"
  )
\end{Sinput}
\end{Schunk}

In the first example, \code{npeaks\_set} is a vector of three integers,
i.e.~the algorithm uses the multi-segment lengths strategy to create the
result object \code{cmps\_with\_multi\_scale}. For
\code{cmps\_without\_multi\_scale} each basis segment is linked to the
top 5 candidate positions. We use \code{include = "full\_result"} to
capture all results. In this example, the CMPS is 9 when using multiple
segments, and 12 when using a single segment. As discussed in
\citet{cmps}, using multi-segment lengths strategy can reduce the number
of false positives when identifying candidate positions; however, any
score based method is walking the line between false positives and false
negatives. As the number of false positives is reduced the number of
false negatives might rise. More discussion and comparisons between the
two versions of the CMPS algorithm will be presented in later sections.
Note, that the multi-segment lengths method is slower because the
algorithm is run once for each segment length.

@@

{\small {}
\begin{Schunk}
\begin{Sinput}
sig_plot <- cmps_signature_plot(
  cmps_with_multi_scale
)
sig_plot$segment_shift_plot
\end{Sinput}
\end{Schunk}
}
\vspace{1em}
\end{minipage}
\begin{minipage}{.59\textwidth}
\includegraphics[width=\textwidth]{ju-hofmann_files/figure-latex/sigplot-1.pdf}
\end{minipage}
\end{adjustbox}
\end{subfigure}
\begin{subfigure}[t]{\textwidth}
\caption{\label{fig:sigplot2}The black line shows the reference signature; the red line shows the comparison signature. Solid part shows the congruent matching profile segments, and the dashed part shows segments that do not agree with the congruent registration position.}
\vspace{1em}
\begin{adjustbox}{valign=t}
\begin{minipage}{.39\textwidth}

{\small {}
\begin{Schunk}
\begin{Sinput}
sig_plot$signature_shift_plot
\end{Sinput}
\end{Schunk}
}
\vspace{1em}
\end{minipage}
\begin{minipage}{.59\textwidth}
\includegraphics[width=\textwidth]{ju-hofmann_files/figure-latex/sigplot2-1.pdf}
\end{minipage}
\end{adjustbox}
\end{subfigure}
\caption{\label{fig:sigplots} Two visual outputs of cmps\_signature\_plot()}
\end{figure}

@@

\begin{Schunk}
\begin{Sinput}
sig_plot$seg_shift
\end{Sinput}
\begin{Soutput}
#>    seg_idx seg_shift
#> 7        7         0
#> 8        8        -1
#> 14      14         5
#> 16      16         8
#> 17      17         8
#> 18      18         8
#> 19      19         9
#> 20      20         9
#> 22      22        12
\end{Soutput}
\end{Schunk}

While \code{cmps\_signature\_plot()} focuses on the signature level,
\code{cmps\_segment\_plot()} focuses on the segment level. It provides
the ``full result'' of \code{extract\_feature\_cmps()}, but also takes
an argument, \code{seg\_idx}, indicating which segment should be
inspected. When checking \code{sig\_plot\$seg\_shift} we notice that
segment number 6 is not one of the congruent matching profile segments.
We can therefore set \code{seg\_idx = 6} in \code{cmps\_segment\_plot()}
and investigate the reason why this segment disagrees with the congruent
registration position.

@@

\begin{itemize}
\tightlist
\item
  \autoref{fig:segplot} is the \code{segment\_plot} for basis segment 6
  at level one (in its original length). We used
  \code{npeaks\_set = c(5, 3, 1)} in \code{extract\_feature\_cmps()}
  when calculating the CMPS score. Therefore the top five peaks are
  identified in the cross-correlation curve at level one. Segment 6 is
  plotted at the positions where these 5 peaks are identified with
  dashed lines in the \code{segment\_plot}. The solid thick black line
  shows the segment at its original position (which in this example is
  very close to the actual registration position).
\item
  \autoref{fig:segplot2} is the \code{scale\_ccf\_plot} of basis segment
  6 at level one. It shows the cross-correlation curve computed by the
  reference signature and the level-one basis segment 6. The five
  highest peaks are marked by dots on the curve.
\end{itemize}

@@

{\small {}
\begin{Schunk}
\begin{Sinput}
seg_plot <- cmps_segment_plot(
  cmps_with_multi_scale,
  seg_idx = 6
)
seg_plot[[1]]$segment_plot
\end{Sinput}
\end{Schunk}
}
\vspace{1em}
\end{minipage}
\begin{minipage}{.59\textwidth}
\includegraphics[width=\textwidth]{ju-hofmann_files/figure-latex/segplot-1.pdf}
\end{minipage}
\end{adjustbox}
\end{subfigure}
\begin{subfigure}[t]{\textwidth}
\caption{\label{fig:segplot2}scale\_ccf\_plot shows the cross-correlation curve between the reference signature and segment 6 at level one. The five highest peaks are marked by dots. The vertical red dashed line indicates the congruent registration position; the green dashed line shows a peak position in the highest segment level; the blue dashed lines show the tolerance zone around the green dashed line. We can see that none of the five highest peaks at level one falls within the tolerance zone, indicating that there is no consistent correlation peak or a candidate position identified by basis segment 6 under the multi-segment lengths strategy. Thus, the basis segment 6 doesn't vote for the congruent registration position and is not a cmps.}
\vspace{1em}
\begin{adjustbox}{valign=t}
\begin{minipage}{.39\textwidth}

{\small {}
\begin{Schunk}
\begin{Sinput}
seg_plot[[1]]$scale_ccf_plot
\end{Sinput}
\end{Schunk}
}
\vspace{1em}
\end{minipage}
\begin{minipage}{.59\textwidth}
\includegraphics[width=\textwidth]{ju-hofmann_files/figure-latex/segplot2-1.pdf}
\end{minipage}
\end{adjustbox}
\end{subfigure}
\caption{\label{fig:segplots} Two plots used to investigate basis segment 6 at level one}
\end{figure}

@@

ggarrange(
  plotlist =
    unlist(seg_plot,
      recursive = FALSE
    ),
  ncol = 2,
  nrow = 3
)
\end{Sinput}
\end{Schunk}
}
\vspace{1em}
\end{minipage}
\begin{minipage}{.59\textwidth}
\includegraphics[width=\textwidth]{ju-hofmann_files/figure-latex/segplot3-1.pdf}
\end{minipage}
\end{adjustbox}
\caption{\label{fig:seg_all} Put segment\_plot and scale\_ccf\_plot of all three levels together. We are identifying five highest peaks at level one, three peaks at level two, and one peak at level three since npeaks\_set = c(5, 3, 1). The highest peak position at level three is marked by the green dashed line across all segment levels. However, the highest peak on level three does not coincide with any of the top five highest peaks at level one. This indicates that there is no consistent correlation peak or a candidate position for basis segment 6 under the multi-segment lengths strategy.}
\end{figure}

@@

\begin{Schunk}
\begin{Sinput}
extract_feature_cmps(
  x, y,
  seg_length = 50,
  Tx = 25,
  npeaks_set = c(5, 3, 1),
  include = "nseg"
)
\end{Sinput}
\end{Schunk}

@@

\caption{Distribution of $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ for Hamby 252; outliers are removed in bullet signatures; \texttt{seg\_length = 50}, \texttt{Tx = 25}, \texttt{npeaks\_set = c(5,3,1)} }\label{fig:result1_252}
\end{figure}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
extract_feature_cmps(
  x, y,
  seg_length = 61,
  Tx = 30,
  npeaks_set = c(5, 3, 1),
  include = "nseg"
)
\end{Sinput}
\end{Schunk}

@@

\caption{Distribution of $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ for Hamby 44; outliers are removed in bullet signatures; \texttt{seg\_length = 61}, \texttt{Tx = 30}, \texttt{npeaks\_set = c(5,3,1)} }\label{fig:result1_44}
\end{figure}
\end{Schunk}

@@

We investigated the effects of different sets of parameters at the
example of both Hamby sets 252 and 44. More specifically, we
investigated the separation achieved using the \pkg{cmpsR}
implementation under various segment lengths (controlled by the
parameter \code{seg\_length}). Specifically, we fixed the parameter
\code{npeaks\_set} that controls the number of peaks at each segment
level to be \code{npeaks\_set = c(5,3,1)} and modified the parameter
\code{seg\_length}. \autoref{fig:param_seg_plot} shows that the default
values of \code{seg\_length} for Hamby 252 and Hamby 44 (50 for Hamby
252 and 61 for Hamby 44, which represent 78.125 \textmu m and 78.69
\textmu m, respectively) result in high values of the sum of squares
ratio, no matter which CMPS metrics are used for an evaluation. However,
we also see, that for Hamby set 252 a basis segment length of 75 is a
better choice than the default segment length; a basis segment length of
122 results in a higher value of sum of squares ratio for Hamby 44.

\autoref{fig:param_npeak_plot} shows results of the CMPS algorithm using
different strategies for identifying peaks in the correlation structure
between signatures. Basis segment length is fixed to the default level
for this evaluation. As can be seen in \autoref{fig:param_npeak_plot},
the default value of \code{npeaks\_set} (\code{npeaks\_set = c(5,3,1)})
leads to promising results in terms of the sum of squares ratio;
however, other choices of \code{npeaks\_set} match and exceed this sum
of squares ratio value.
